Embeddings and Attention in Predictive Modeling

### 2022-03-27 manuscript/manuscript.Rmd
address 'nothing more than a glm' comment
add comment about being careful w/ train/validation split for embedding training -> glm

If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM. A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we discuss in more detail next.

@@

>>>>

If $K$ is set equal to $1$, then Equation \ref{NN} reduces to a form similar to the GLM, where $\sigma$ is analogous to the link function and $a_1X+b_1$ the linear predictor. A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we discuss in more detail next.

@@

Regardless of the hyperparameters chosen, care needs to be taken in ensuring the integrity of the model validation process, since when we train
the embeddings, we utilize the information from the response variables. Therefore, the holdout data must not be seen by the neural network
training process or the GLM fitting process.
